---
title: "ST558 Project 1"
author: "Aries Zhou"
date: "10/3/2021"
---

```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("./ST558_Proj_1.Rmd", 
                  output_format = "github_document", 
                  output_dir = "../ywzhou33.github.io/_posts/",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.align='center', fig.path = "../ywzhou33.github.io/images/")
```

[The link to Github Pages repo: ](https://github.com/ywzhou33/ST558-Project-1.git)  
[The link to Github Blog repo: ](https://github.com/ywzhou33/ywzhou33.github.io.git)  

```{r Packages, echo=TRUE}
library(httr)
library(jsonlite)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
```

##Connects to the One Call API.  

Parameters:

 - `lat` `(required)` - Latitude; geographical coordinates that have values between -180 and 180.  
 - `lon` `(required)` - Longitude; geographical coordinates that have values between -180 and 180.  
 - `appid` `(required)` - Your unique API key  
 - `exclude` `(optional)` - You can use it to exclude some parts from the data, available values are `current`, `minutely`, `hourly`, `daily`, `alerts`, should be a comma-delimited list (without spaces).  
 - `units` `(optional)` - Units of measurement. `standard` (Kelvin & meter/sec), `metric` (Celsius & meter/sec) and `imperial` (Fahrenheit & miles/hour) units are available. If you do not use the `units` parameter, `standard` units will be applied by default.  
 - `lang` `(optinal)` - You can use this parameter to get the output in your language.  

```{r API, echo=TRUE}
#To get access to current weather, minute forecast for 1 hour, hourly forecast for 48 hours, daily forecast for 7 days and government weather alerts
seq(from = -180, to = 180, by = 50.66)
lat <- 35.78
lon <- c(-78, 180)
exclude <- "current,minutely,hourly"
units <- "metric"
appid <- "1f302e9647903cb7b350a5580d5c00dc" 
"6U4chzdkpf2hc4b5jNwsmkN07rhH4OWC" # API key

get.URL <- function(lat, lon, appid, exclude, units, lang){
        if (is.null(lat)){
        URL <- paste("https://api.openweathermap.org/data/2.5/onecall?", lat)    
        }
        if (is.null(lon)){
        URL <- paste("https://api.openweathermap.org/data/2.5/onecall?", lat, lon, sep = "&")    
        }
        if (is.null(appid)){
        URL <- paste("https://api.openweathermap.org/data/2.5/onecall?", lat, lon, appid, sep = "&")
        }
        else{
        URL <- paste("https://api.openweathermap.org/data/2.5/onecall?", lat, lon, tolower(exclude), appid, sep = "&")
        }
        URL
}
Test <- get.URL(lon,appid,exclude,units)        

URL <- c("https://api.openweathermap.org/data/2.5/onecall?lat=35.78&lon=-78.68&exclude=current,minutely,hourly&units=metric&appid=1f302e9647903cb7b350a5580d5c00dc", "https://api.openweathermap.org/data/2.5/onecall?lat=35.78&lon=180&exclude=current,minutely,hourly&units=metric&appid=1f302e9647903cb7b350a5580d5c00dc")


for (i in 1:length(URL)) {
Data.raw <- httr::GET(URL[i])
str(Data.raw, max.level = 1)
Data.F7 <- Data.raw$content %>% rawToChar() %>% fromJSON()
#return(Data.F7[["daily"]])
}

#get.data <- function(URL){}
```

Get data
```{r Data, echo=TRUE}
URL.1 <- "https://api.openweathermap.org/data/2.5/onecall?lat=35.78&lon=-78.68&exclude=current,minutely,hourly&units=metric&appid=1f302e9647903cb7b350a5580d5c00dc"
Data.raw.1 <- httr::GET(URL.1)
str(Data.raw.1, max.level = 1)
Data.1 <- Data.raw.1$content %>% rawToChar() %>% fromJSON()

URL.2 <- "https://api.openweathermap.org/data/2.5/onecall?lat=35.78&lon=-180&exclude=current,minutely,hourly&units=metric&appid=1f302e9647903cb7b350a5580d5c00dc"
Data.raw.2 <- httr::GET(URL.2)
str(Data.raw.2, max.level = 1)
Data.2 <- Data.raw.2$content %>% rawToChar() %>% fromJSON()

Data.1.a <- Data.1[["daily"]] %>% select(dt, pressure:dew_point, starts_with("wind"), rain)

Data.1.b <- data.frame(Data.1[["daily"]]$temp[2], Data.1[["daily"]]$temp[3], Data.1[["daily"]]$feels_like[1], Data.1[2])

Data.1.new <- cbind(Data.1.a, Data.1.b)

Data.2.a <- Data.2[["daily"]] %>% select(dt, pressure:dew_point, starts_with("wind"), rain)

Data.2.b <- data.frame(Data.2[["daily"]]$temp[2], Data.2[["daily"]]$temp[3], Data.2[["daily"]]$feels_like[1], Data.2[2]) 

Data.2.new <- cbind(Data.2.a, Data.2.b)

Full.data <- rbind(Data.1.new, Data.2.new)
```

```{r NewVar, echo=TRUE}
weather <- Full.data %>% 
        mutate(area = if_else((lon>=-120.74)&(lon<=-75.59), "Land", 
                      if_else((lon>=-5.91)&(lon<=120.44), "Land", "Water")),
               wind_status = if_else(wind_speed>=8.9, "Windy", 
                      if_else(wind_speed>=6.7, "Breezy", "Clam")),
               temp_day = (min+max)/2) %>% 
        as_tibble()  
#group_by(area) %>% summarise(temp_avg = mean(temp_day), rain_avg = mean(rain))
```

Graphical Summaries  

```{r histogram, echo=TRUE}
#Histogram for Temperature
his_temp <- ggplot(data = weather, aes(x = temp_day))
his_temp + geom_histogram(aes(fill = as.factor(area))) +
           geom_density(aes(fill = as.factor(area)))+ 
  labs(x="Average Daily Temperature", title = "Histogram for Temperature") + 
  scale_fill_discrete(name = "Area")
```

```{r boxplot_temp, echo=TRUE}
#boxplot for temperature
box_temp <- ggplot(data = weather, aes(x = temp_day))
box_temp + geom_boxplot(aes(y = as.factor(area))) + 
  geom_jitter(aes(x = temp_day, y = as.factor(area), color = as.factor(area))) + 
labs(x ="Temperature", y ="Area", title = "Boxplot for Temperature") +
scale_color_discrete(name = "Area") + 
coord_flip() 
```

```{r bar_chart, echo=TRUE}
#barchart for Wind Status
bar_wind <- ggplot(data = weather, aes(x = as.character(wind_status)))
bar_wind + geom_bar(aes(fill = as.factor(area)), position = "dodge") + 
  labs(x="Wind Status", title = "Bar Chart for Wind Status") + 
  scale_fill_discrete(name = "Area")
```

```{r boxplot_hum, echo=TRUE}
#boxplot for humidity
box_hum <- ggplot(data = weather, aes(x = humidity))
box_hum + geom_boxplot(aes(y = as.factor(area))) + 
  geom_jitter(aes(x = humidity, y = as.factor(area), color = as.factor(area))) + 
labs(x ="Humidity", y ="Area", title = "Boxplot for Humidity") +
scale_color_discrete(name = "Area") + 
coord_flip()
```


```{r scatter, echo=TRUE}
correlation <- cor(weather$wind_speed, weather$humidity)
correlation

#Scatterplot for Wind Status v.s. Humidity.
scatter <- ggplot(data = weather, aes(x = wind_speed, y = humidity))
scatter + geom_point(aes(color = as.factor(wind_status), shape = as.factor(area))) + 
geom_smooth(method = lm) + 
labs(title = "Wind Speed vs Humidity", x = "Wind Speed", y = "Humidity") + 
scale_color_discrete(name = "Wind Status") +
scale_shape_discrete(name = "Area")
```

