---
title: "ST558 Project 1"
author: "Aries Zhou"
date: "10/3/2021"
---

```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("./ST558_Proj_1.Rmd", 
                  output_format = "github_document", 
                  output_dir = "../ywzhou33.github.io/_posts/",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.path = "../ywzhou33.github.io/images/")
```

[The link to Github Pages repo: ](https://github.com/ywzhou33/ST558-Project-1.git)  
[The link to Github Blog repo: ](https://github.com/ywzhou33/ywzhou33.github.io.git)  

```{r Packages, echo=TRUE}
library(devtools)
library(bigrquery) 
library(DBI)
library(httr)
library(jsonlite)
```

##Connects to the API.  

Parameters:

 - `q` `(required)` - City name, state code and country code divided by comma.  
 - `appid` `(required)` - Your unique API key  
 - `mode` `(optional)` - Response format. Possible values are `xml` and `html`. If you don't use the mode parameter format is JSON by default.  
 - `units` `(optional)` - Units of measurement. `standard`, `metric` and `imperial` units are available. If you do not use the `units` parameter, `standard` units will be applied by default.  
 - `lang` `(optinal)` - You can use this parameter to get the output in your language.  

```{r API, echo=TRUE}
#https://api.openweathermap.org/data/2.5/onecall?lat=33.44&lon=-94.04&exclude=hourly,daily&appid={API key}

key <- "1f302e9647903cb7b350a5580d5c00dc" 
"6U4chzdkpf2hc4b5jNwsmkN07rhH4OWC" # API key
get.URL <- function(q, appid, mode, units, lang){
 
}
URL <- "https://api.openweathermap.org/data/2.5/onecall?lat=35.78&lon=-78.68&appid=1f302e9647903cb7b350a5580d5c00dc"

NCSU <- httr::GET(URL)
str(httr::content(NCSU), max.level = 1)
NCSU_txt <- httr::content(NCSU, "text")

```



