---
title: "ST558 Project 1"
author: "Aries Zhou"
date: "10/3/2021"
---

```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("./ST558_Proj_1.Rmd", 
                  output_format = "github_document", 
                  output_dir = "./",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, fig.align='center')
```

#### Listing the packages used in this prject.  

```{r Packages, echo=TRUE}
library(httr)
library(jsonlite)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
```

#### Connects to the One Call API.  

The One Call API provides the following weather data for any geographical coordinates:  
 - Current weather  
 - Minute forecast for 1 hour  
 - Hourly forecast for 48 hours  
 - Daily forecast for 7 days  
 - National weather alerts  
 - Historical weather data for the previous 5 days  

These data can be accessed by defining the following parameters in the URL.

Parameters:

 - `lat` `(required)` - Latitude; geographical coordinates that have values between -180 and 180.  
 - `lon` `(required)` - Longitude; geographical coordinates that have values between -180 and 180.  
 - `appid` `(required)` - Your unique API key  
 - `exclude` `(optional)` - You can use it to exclude some parts from the data, available values are `current`, `minutely`, `hourly`, `daily`, `alerts`, should be a comma-delimited list (without spaces).  
 - `units` `(optional)` - Units of measurement. `standard` (Kelvin & meter/sec), `metric` (Celsius & meter/sec) and `imperial` (Fahrenheit & miles/hour) units are available. If you do not use the `units` parameter, `standard` units will be applied by default.  
 - `lang` `(optinal)` - You can use this parameter to get the output in your language.  

This section of code is written to get access to daily forecast for 7 days and government weather alerts around the globe at latitude 35.78 (where the North Carolina State University is located). Multiple URLs are returned with the `get.URL` function. Then the data accessed with the URLS are parsed and saved into a list called `Data.F7`.  

```{r API.URL, echo=TRUE}
#Define values for the parameters
lat <- 35.78
lon <- seq(from = -180, to = 180, by = 4.3)
exclude <- "current,minutely,hourly"
units <- "metric"
appid <- "411f596c9a67840a793286c1f7f3d0c1" # API key

#Function to get a vector containing a list of URL to request datasets from API.
get.URL <- function(lat, lon, appid, exclude=NULL, units = NULL, lang = NULL, ...){
        base_url<- "https://api.openweathermap.org/data/2.5/onecall?"
        if (is.null(lat)){
        URL <- paste(base_url, "lat=", lat, sep = "")    
        }
        if (is.null(lon)){
        URL <- paste(base_url, "lat=", lat, "&lon=", lon, sep = "")    
        }
        if (is.null(appid)){
        URL <- paste(base_url, "lat=", lat, "&lon=", lon, "&appid=", appid, sep = "")
        }
        if (is.null(exclude)){
        URL <- paste(base_url, "lat=", lat, "&lon=", lon, "&exclude=", tolower(exclude), "&appid=", appid, sep = "")
        }
        if (is.null(units)){
        URL <- paste(base_url, "lat=", lat, "&lon=", lon, "&exclude=", tolower(exclude), "&units=", units, "&appid=", appid, sep = "")
        }
        if (is.null(lang)){
        URL <- paste(base_url, "lat=", lat, "&lon=", lon, "&exclude=", tolower(exclude), "&units=", units, "&appid=", appid, sep = "")
        }
        else{
        return("Error: Invalid input")
        }
        URL
}

#Call the function to get URLs
URL <- get.URL(lat=lat, lon=lon, appid=appid, exclude=exclude, units=units)        

#Use for loop to get a list of data parsed from API and save them into an object called Data.F7.
Data.raw <- list()
Data.F7 <- list()

for (i in 1:length(URL)) {
j <- i
Data.raw[[j]] <- httr::GET(URL[i])
Data.F7[[j]] <- Data.raw[[j]]$content %>% rawToChar() %>% fromJSON()
}
```

#### Data Manipulation  

Create a `select.data` function to choose the parts I want from each listed data from API.  

```{r Small.Data, echo=TRUE}
select.data <- function(Data.F7, k){
        Data.a <- Data.F7[[k]][["daily"]] %>% 
            select(dt, pressure:dew_point, starts_with("wind"))
        Data.b <- data.frame(Data.F7[[k]][["daily"]]$temp[2], 
                      Data.F7[[k]][["daily"]]$temp[3], 
                      Data.F7[[k]][["daily"]]$feels_like[1], 
                      Data.F7[[k]][2])
        Data.ab <- cbind(Data.a, Data.b)
        return(Data.ab) #return a horizontally combined data form one URl
}
```

Call the `select.data` function inside the `get.full.data` function to combine all samll datasets togeter.  

```{r Full.Data, echo=TRUE}
get.full.data <- function(Data){
  Data.a <- data.frame()
  Data.b <- data.frame()
  Full.data <- data.frame()

  for (k in 1:length(Data)){
    New.data <- select.data(Data, k)
    Full.data <- bind_rows(New.data, Full.data, )
  }
  return(Full.data) #return a vertically combined full data form all URls 
}

#called the get.full.data function to get a dataframe containing all datasets together.
Full.data  <- get.full.data(Data = Data.F7)
```

Creating two categorical variables and some statistics.  

```{r New.Var, echo=TRUE}
weather <- Full.data %>% 
        mutate(area = if_else((lon>=-120.74)&(lon<=-75.59), "Land", 
                      if_else((lon>=-5.91)&(lon<=120.44), "Land", "Water")), # divide the data into land area and water/ocean area according to the longitude values. 
               wind.status = if_else(wind_speed>=8.9, "Windy", 
                      if_else(wind_speed>=6.7, "Breezy", "Clam")), # define the wind status.
               temp.day = (min+max)/2) %>% # calculate the average  daily temperature.
        as_tibble()  
```

```{r Explore.Data, echo=TRUE}
#Take a look at the data, only showing the first 10 observations.
knitr::kable(head(weather, n = 10))

#Create a contingency table for area and wind status.
knitr::kable(table(weather$area, weather$wind.status))
```

#### Graphical Summaries   

Below is a histogram that shows the distribution of the average forecasting temperature of future 7 days for the land and water/ocean area around the globe at latitude of 35.78. From the graph, I observed that the distributions of average temperature are highly skewed for both land and water area. The water area tend to have higher daily temperature in the future 7 days.    

```{r histogram, echo=TRUE}
#Histogram for Temperature
his.temp <- ggplot(data = weather, aes(x = temp.day))
his.temp + geom_histogram(aes(fill = as.factor(area))) +
  labs(x="Average Daily Temperature", title = "Histogram for Temperature") + 
  scale_fill_discrete(name = "Area")
```

Below is a boxplot that shows the distribution of the average daily temperature for the land and water/ocean area around the globe at latitude of 35.78. It confirms the trends displayed in the histogram that the distributions of average temperature are highly skewed for both areas. The water area tend to have higher average daily temperature in the future 7 days.

```{r boxplot_temp, echo=TRUE}
#Boxplot for Temperature
box.temp <- ggplot(data = weather, aes(x = temp.day))
box.temp + geom_boxplot(aes(y = as.factor(area))) + 
  geom_jitter(aes(x = temp.day, y = as.factor(area), color = as.factor(area))) + 
labs(x ="Temperature", y ="Area", title = "Boxplot for Temperature") +
scale_color_discrete(name = "Area") + 
coord_flip() 
```
From the barchart below, I found that the wind status on the land area is more calm while it is more windy over the water area across the globe at latitude 35.78 for the future 7 days.  

```{r bar_chart, echo=TRUE}
#barchart for Wind Status
bar.wind <- ggplot(data = weather, aes(x = as.character(wind.status)))
bar.wind + geom_bar(aes(fill = as.factor(area)), position = "dodge") + 
  labs(x="Wind Status", title = "Bar Chart for Wind Status") + 
  scale_fill_discrete(name = "Area")
```
This boxplot indicates that the humidity over the water areas is higher in general than that on the land areas and the humidity varies more on the land areas.  

```{r boxplot_hum, echo=TRUE}
#boxplot for humidity
box.hum <- ggplot(data = weather, aes(x = humidity))
box.hum + geom_boxplot(aes(y = as.factor(area))) + 
  geom_jitter(aes(x = humidity, y = as.factor(area), color = as.factor(area))) + 
labs(x ="Humidity", y ="Area", title = "Boxplot for Humidity") +
scale_color_discrete(name = "Area") + 
coord_flip()
```

This scatter plot indicates that there is a slight positive correlation relationship between the temperature and humidity. Warm air tend to hold more vapor than cool air.     

```{r scatter, echo=TRUE}
correlation <- cor(weather$temp.day, weather$humidity)
knitr::kable(correlation)

#Scatterplot for Wind Status v.s. Humidity.
scatter <- ggplot(data = weather, aes(x = temp.day, y = humidity))
scatter + geom_point(aes(color = as.factor(wind.status), shape = as.factor(area))) + 
geom_smooth(method = lm) + 
labs(title = "Avery Daily Temperature vs Humidity", x = "Avery Daily Temperature", y = "Humidity") + 
scale_color_discrete(name = "Wind Status") +
scale_shape_discrete(name = "Area")
```

